---
title: "R Notebook"
output: html_notebook
---

---
 title: "Review KNN Assigment"
author:     Niek 
Reviewer:   Hai
---

```{r}
library(tidyverse)
library(googlesheets4)
library(class)
library(caret)
```


## Business Understanding
By using multiple variable i am going to predict if the room is occupied or not.



## Data Understanding
```{r}
url <- "https://raw.githubusercontent.com/HAN-M3DM-Data-Mining/data-mining-s2y2122-Goodstudent101/master/datasets/KNN-occupancy.csv"
Dataset <- read_csv(url)
```



## Data Preparation
```{r}
model<-lm( Occupancy ~ CO2 + Light + Temperature + date,data=Dataset)
summary(model1)
```
## Ok ##

```{r}
Test2.0 <- table(Dataset$Occupancy)

Test3.0u <- round(prop.table(cntOccu) * 100 , digits = 1)

cleanDF$Occupancy <- factor(Dataset$Occupancy, levels = c(0, 1))
```
## Hai's comment: I think you lack of the normalize step to normalize numeric fearure for testing##

```{r}
Test4.0 <- cleanDF[1:4071,  ]

Test5.0<- cleanDF[4072:8143,  ]
```
## Hai: Test4.0 and 5.0 is the training and tesing dataset##

```{r}
Test6.0<- cleanDF[1:4071,  3]

Test7.0 <- cleanDF[4072:8143,  3]
```
## Also same for this with the dataset with labels##


## Modeling
```{r}
model2.0 <- knn(train = as.matrix(Test4.0), test = as.matrix(Test5.0), cl = as.matrix(Test6.0), k = 21)

head(cleanDF_occupancy_pred)
```
## Hai: I ran into a problem: Warning in knn(train = as.matrix(Test4.0), test = as.matrix(Test5.0), cl = as.matrix(Test6.0),  :  NAs introduced by coercion ##

```{r}
Tabel2.0 <- factor(KNN_occupancy$Occupancy, levels = c("0", "1"), labels = c("unoccupied", "Occupied")) %>% relevel("Occupied")
head(KNN_occupancy, 50)
```

##Hai: Also here the 'KNN_occupancy' not found##

## Evaluation and Deployment
```{r}
confusionMatrix(cleanDF_occupancy_pred, testDF_labels[[1]], positive = NULL, dnn = c("Prediction", "True"))
```
## Hai: Some variables are not found:'cleanDF_occupancy_pred', which lead to the misunderstanding of the system and so the file can not run##
